%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Sakeeb}{Hossain}{ \urlstyle{same}\url{www.sakeebhossain.me} \\
\href{mailto:sakeeb.hossain@mail.utoronto.ca}{sakeeb.hossain@mail.utoronto.ca} | 416.438.6167
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     CONTENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}{0.80\textwidth}
\leavevmode \newline
\leavevmode \newline

Mr. Gob Bluth
\hspace{53ex} Monday, May 8th, 2017\\                    
Campus Recruiter \\
Shopify \\
80 Spadina Avenue, 4th Floor \\
Toronto, ON \\
M5V 2J4 \\
\sectionsep

\end{minipage}

\leavevmode \newline

\begin{minipage}{0.80\textwidth}

Dear Gob Bluth,\\

I am pleased to be presented with this this opportunity to work with Shopify as a Software Developer Intern, as advertised on the University of Toronto Scarborough website. I was very excited to see this position listed because I’ve always been passionate about using software in creative ways to solve real-world problems. I believe this position would provide an excellent opportunity to do just that, all while working with one of the most innovative tech companies in Canada. As a driven, and ambitious developer, I believe my ability to learn quickly and my proven experience working efficiently with a development team makes me an excellent candidate to make an impact and get *insert poop emoji here* done at Shopify.\\

I am proficient with JavaScript, Python and a variety of web frameworks and am always eager to learn more. I am also especially passionate about using software to help innovate our daily lives. An example of this would be when I wrote a web-scraper that gathered detailed course information and presented it in a useful and organized way. I then created a website where I regularly put up the information to make it accessible to other and today, the application has been used by 1000s of students. I also helped create a website for Heart and Stroke UTSC (a university club), where I designed a website to advertise the club using Bootstrap and JavaScript, including features such as such as an events calendar, email form and photo gallery. Through my experiences working on these projects, I have developed a sharp attention to detail and a strong programmer’s intuition. \\

I also have professional experience with web development working at the Ministry of Government Services, where I helped redesign their internal media development service. Specifically, I designed an interactive webapp with Angular, jQuery and JWPlayer which allowed users to customize a video and then generated an embed code which users could use on other intranet sites. \\

As an enthusiastic, inquisitive and experienced developer, I believe I would be an excellent addition to Shopify’s development team. I look forward to meeting with you in person to further discuss my suitability for this position. Thank you for your valuable time and consideration. \\

Regards,\\
Sakeeb Hossain \\

\leavevmode \newline

P.S. I used \LaTeX \space to format this, so alas, I couldn't use emojis. So, to make up for it, I drew the owl! Check it out here: http://imgur.com/a/GieR6.

\end{minipage}

\end{document}  \documentclass[]{article}