%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Ahnaf}{Hossain}{ \urlstyle{same}\url{http://sakeebhossain.me} \\
\href{mailto:sakeeb.hossain@mail.utoronto.ca}{sakeeb.hossain@mail.utoronto.ca} | 416.438.6167
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of Toronto}
\descript{Bachelors in Computer Science}
Software Engineering Stream\\
\location{Expected May 2019 | Toronto, ON}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Proficient}
Python \textbullet{}   JavaScript \textbullet{} Java \textbullet{} C \\
Bash \textbullet{} HTML \textbullet{} CSS \\ 
\location{Experience}
PHP \textbullet{} Flask \textbullet{} MySQL \textbullet{} R \textbullet{} Assembly \\
\location{Frameworks \& Technologies:}
Flask \textbullet{} BootStrap \textbullet{} Android \textbullet{} Git
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
\subsection{Areas of Comp. Science}
Graph Theory \\
Big Data\\
Machine Learning \\
Security \& Cryptography \\
Graph Theory \\
\location{Favorite Algorithm:}
Ford-Fulkerson (Max-Flow Min-Cut)
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
\href{https://github.com/sakeebhossain}{\custombold{github}.com/sakeebhossain} \\
\href{https://www.linkedin.com/in/sakeebhossain}{\custombold{linkedin}.com/in/sakeebhossain} \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EMPLOYMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Employment}

\runsubsection{CIBC}
\descript{| Application Developer }
\location{Electronic Financial Transactions Team | Jan 2017 – Apr 2017 | Toronto, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Reduced time needed to generate hourly ATM uptime report by over 20\% by optimizing SQL queries.
\item Wrote a Bash script that runs queries looking for flagged transactions. Set up cron job to regularly email this report to production support team.
\item Performed SOA testing for new services, querying a database and checking log files to ensure there was no irregular behavior.
\item Debugged a variety of C scripts, and participated in code reviews.
\end{tightemize}
\sectionsep

\runsubsection{Ministry of Government Services}
\descript{| Web Developer}
\location{ Media Delivery Service Team | May 2016 – Aug 2016 | Toronto, ON}
\begin{tightemize}
\item Upgraded web player from Flash to JW Player to add support HTML5 video.
\item Created web app in jQuery and PHP that loads a video with setting specified by the user (resolution, caption language, described audio, etc.). Parses XML files to gather sources for specified settings.
\item Wrote automated tests using Jasmine JS framework to test websites for compliance to design and accessibility guidlines.
\item Gained experience with Agile and SCRUM development methodologies.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PERSONAL PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal Projects}
\runsubsection{LeapText}
\descript{| Desktop Application}
\begin{tightemize}
\item Allow users to write and erase text with hand gestures by capturing movement with LeapMotion sensor, and then allowing the user to post the message to Facebook or Twitter with a swipe. 
\item Used Google Cloud Vision API to detect text in user drawings, as well as Facebook and Twitter APIs to publish posts. Used Node.js for backend.
\item Winner of "The Hub Creative Hack" prize at HackTheValley.
\end{tightemize}
\sectionsep

\runsubsection{fillme.org}
\descript{| Web Application}
\begin{tightemize}
\item A tool that helps students fill their class schedules by filtering by criteria such as day of the week, time, discipline and year level.
\item Wrote web scraper using Python's request and BeautifulSoup libraries.
\end{tightemize}
\sectionsep

\runsubsection{Meerar}
\descript{| Web Application}
\begin{tightemize}
\item A site that gives career advice by analyzing journal logs from users.
\item Used Lexalytics Sentiment analysis API to assign mood scores and handled backend with Flask and MySQL to store user data.
\item Winner of Lexalytics API prize and CPS prize at McHacks 2017.
\end{tightemize}
\sectionsep

\runsubsection{Wikipedia Game Bot}
\descript{| Web Crawler}
\begin{tightemize}
\item Uses Breadth First Search to find the shortest path from a given wiki article to the "Philosophy" wiki article by following hyperlinks. 
\item Designed selection algorithms to prevent infinite looping.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{ACHIEVEMENTS} 
\begin{tabular}{rll}
2017	     & 3rd Place Microsoft Coding Competition @ UofToronto\\
2016	     & 2nd Place at UTSC FinanceHacks\\

\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}